Smart Model Elimination for Efficient Automated Machine Learning in Healthcare

### 2024-06-27 paper/paper.tex
small changes

Machine learning (ML) algorithms require complicated processes like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning. To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks. These frameworks create comfortable environments for models to excel in. They handle missing values, preprocess data, and optimize training to ensure the best results [1].

@@

\section{Evaluation}
\subsection{Experiment Design}
To evaluate our framework, we choose 5 different datasets of diverse size. We ran SMEML on each dataset for 20 iterations of tuning. We compared this against a "dumb" mode which simply runs every model on the dataset. We used the accuracy and time to train as our metrics. All experiments are run on an Ubuntu server with Intel Xeon E5520 @ 2.27GHz and 24GB of RAM.

>>>>

Machine learning (ML) algorithms require complicated processes like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning. To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks. These frameworks automate the complicated processes of producing effective ML models, making it more accessable to non-experts. They handle missing values, preprocess data, and optimize training to ensure the best results [1].

@@

\section{Evaluation}
\subsection{Experiment Design}
To evaluate our framework, we choose six different datasets of diverse size. We ran SMEML on each dataset for 20 iterations of tuning. We compared this against a "dumb" mode which simply runs every model on the dataset. We used the accuracy and time to train as our metrics. All experiments are run on an Ubuntu server with Intel Xeon E5520 @ 2.27GHz and 24GB of RAM.
